---
title: "R Notebook"
output: html_notebook
date: 9 November 2020
---


Downloading csv file from Kaggle Data set - https://www.kaggle.com/austinreese/craigslist-carstrucks-data

```{r}
library(dplyr)
library(rpart)
carData <- read.csv("/Users/rebeccahousey/Documents/GitHub/UsedCarRepo/vehicles.csv", header = TRUE, sep = ',' ,na.strings = "", stringsAsFactors = FALSE)
#str(vehicles)

```
Cleaning data (1)
- removing 'cylinders' in cylinders column 
- removing id, url, region_url, county columns, image_url, description, vin (irrelevant)
- removing NAs 
- changing year to age of car

```{r} 
carData$cylinders <- gsub('cylinders', "", paste(carData$cylinders))
carData <- select(carData, -c(id, url, region_url, county, image_url, description, vin, model))
carData <- na.omit(carData)
carData[carData == 'NA'] <- NA
carData <- na.omit(carData)
carData %>% mutate(age = 2020-year) %>% select(-year) -> vehicles
carData<-carData[complete.cases(carData),]
carData <- data.frame(lapply(carData, as.factor))
carData <- data.frame(lapply(carData, as.factor))


```


Plotting to see correlations between price and other variables
1) There is a high correlation between price and transmission, 
```{r}
library(ggplot2)
#library(plot)


ggplot(data = carData, aes(condition, price)) + geom_jitter(color = "blue", alpha = 0.5) + theme_light() + scale_y_log10()
 

ggplot(data = carData, aes(condition, price)) + geom_jitter(color = "blue", alpha = 0.5) + theme_light() + scale_y_log10()
 
ggplot(data = carData, aes(paint_color, price)) + geom_jitter(color = "blue", alpha = 0.05) + theme_light() + ylim(4000,100000)

vehicles %>% ggplot(aes(transmission, price))+geom_boxplot()+geom_jitter(alpha=0.05)+ ylim(4000,100000)
ggplot(data = carData, aes(model, price)) + geom_jitter(color = "blue", alpha = 0.05) + theme_light() + ylim(4000,100000)



```
Splitting up the data 
Training and Testing Data to use 80% training 20% testing
```{r}
split <- sort(sample(nrow(carData), nrow(carData)*.8))
trainingCar <- carData[split,]
testCar <- carData[-split,]
```
Creating Models 
1) Regression Trees: Getting 
2) MLR - Multiple Linear Regression
```{r}
#ADD IN MULTIPLE LINEAR REGRESSION HERE(MLR) and regression tree


library(rpart)
library(caTools)
set.seed(123)
str(carData)
Predicing Price with odometer and year
DF <- data.frame(trainingCar$year, trainingCar$odometer)
split1 <- sort(sample(nrow))
tree_model<- rpart(price ~ ., data = trainingCar)
``` 

```{r}
#R - square for Regression Tree



tree_pred = predict(tree_model, newdata=testCar)
SSE <- sum((tree_pred-testCar$price)^2)
SST <- sum(testCar$price, mean(testCar$price)^2)
R_square <- 1- SSE/SST
RMSE <- sqrt(SSE/nrow(carData))
R_square


#getting mean square error
mape <- mean(abs((real_preds$predicteds - real_preds$actuals))/real_preds$actuals)
mse <- mean((testCar$price-pred_value)^2)
mse
```






